Navigating to a greener Europe with 24/7 hourly carbon-free electricity procurement

### 2023-10-14 manuscript/sections/conclusion.tex
manuscript: add conclusions

Taken together, we show that 24/7-CFE commitment by corporate sector stakeholders is a step above and beyond the 100\% annual renewable matching in paving the path toward the carbon net-zero energy systems. 
This voluntary commitment also delivers a range of benefits to the society by 
(i) triggering innovation, availability and earlier utilisation of advanced clean firm generation needed for the transformation of energy systems to a complete carbon net-zero state, 
(ii) reducing system emissions, and (iii) reducing system flexibility needs.

>>>>

24/7 carbon-free energy matching is a viable and effective strategy for electricity buyers aiming to eliminate their own carbon footprint and contribute to wider system decarbonisation.
Voluntary commitments to 24/7 CFE procurement have further transformative effect on electricity systems through accelerated innovation and early deployment of advanced energy technologies.
The evidence holds across geographical locations and time periods, and is robust to sensitivity analyses.
The strategy retains its significance in reducing system-level emissions, even as grids become cleaner over time, which is essential in light of evolving national energy and climate policies.

### 2023-10-14 manuscript/sections/discussion.tex
manuscript: add conclusions

More work---encompassing the collective contributions of the research community, \gls{ngo}s, policy-makers, and corporate energy buyers---is needed to deepen our understanding of the implications, challenges, and opportunities inherent in various clean energy procurement strategies, guiding us all towards net-zero sustainable energy systems.

>>>>

More work---encompassing the collective contributions of the research community, \gls{ngo}s, policy-makers, and corporate energy buyers---is needed to deepen our understanding of the implications, challenges, and opportunities inherent in various clean energy accounting approaches and procurement strategies, guiding us all towards net-zero sustainable energy systems.
